---
title: "Kershaw, Scherzer, Price, Hamels"
author: "Derek Sollberger"
date: "8/4/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("kableExtra")
library("tidyverse")
```

Just for fun, I want to compute a line of statistics for the Dodgers' pitchers Clayton Kershaw, Max Scherzer, David Price, and Cole Hamels; but back in the 2011, 2012 and 2013 seasons (arguably when they were in their prime and winning Cy Young awards).

# Data

Source: Baseball Reference

* https://www.baseball-reference.com/players/k/kershcl01.shtml
* https://www.baseball-reference.com/players/s/scherma01.shtml
* https://www.baseball-reference.com/players/p/priceda01.shtml
* https://www.baseball-reference.com/players/h/hamelco01.shtml

```{r, message = FALSE, warning = FALSE}
pitcher_df <- read_csv("pitcher_data.csv")
```

```{r}
pitcher_df %>%
  kbl() %>%
  kable_paper("hover", full_width = F)
```

# Baseball Stats

Next, I want to add up the pitchers' stats by season and compute the ERA (earned run average)

```{r}
pitcher_sums <- pitcher_df %>%
  group_by(season) %>%
  summarize(totalW = sum(W),
            totalL = sum(L),
            totalER = sum(ER),
            totalIP = sum(IP))

pitcher_sums <- pitcher_sums %>%
  mutate(ERA = 9*totalER / totalIP)
```

Now let us condense the information for a tweet

```{r}
display_df <- pitcher_sums %>% select(season, totalW, totalL, ERA)

colnames(display_df) <- c("season", "W", "L", "ERA")

display_df %>%
  kbl() %>%
  kable_paper("hover", full_width = F)
```

