---
title: "Passing Variables"
author: "Derek Sollberger"
date: "9/13/2021"
output: html_document
---

```{r, message = FALSE, warning = FALSE}
library("palmerpenguins")
library("patchwork")
library("tidyverse")
```

For a project, I finally needed to learn how to pass column names for `ggplot` and `dplyr` commands.  Here, I will try out these ideas on the `penguins` data set from the `palmerpenguins` package.

```{r}
str(penguins)
df <- penguins #prefer to make a copy
df$year <- factor(df$year,
                  levels = c("2007", "2008", "2009"))
```

Let us make boxplots, but over the 4 categorical variables: `species`, `island`, `sex`, and `year`.  Normally, I would make one graph, copy-and-paste, and change the variable names manually.

What if we made a skeleton code block?

```{r}
boxplot_by_group <- function(data, metric, group){
  data %>%
    ggplot(aes(x = .data[[group]], y = .data[[metric]],
               fill = .data[[group]])) +
    geom_boxplot(color = "black") +
    theme_minimal()
}
```

For now, it seems that using `.data[[_____]]` with carefully worded local variables does the job well.  Then perhaps we can make 4 graphs simply with

```{r}
p1 <- boxplot_by_group(df, "flipper_length_mm", "species")
p2 <- boxplot_by_group(df, "flipper_length_mm", "island")
p3 <- boxplot_by_group(df, "flipper_length_mm", "sex")
p4 <- boxplot_by_group(df, "flipper_length_mm", "year")
```

Finally, here is our `patchwork` image.

```{r}
(p1 + p2) / (p3 + p4)
```

